### 2021-07-06 chapters/rq2/1_experiment_design.tex
discussion without threats to validity
fixed wrong cite

\subsection{Algorithm parameters}
The fuzzy c-means algorithm has to initialize the centroids of the clusters.
Our selected library does this based on a random number.
It also allows us to control this random number.
To make the initialization of the centroid reproducible and deterministic we will use a generated seed.
The seed generated is included in the Github repository\cite{rbasarat-repo}.
\newline
Bezdek et al., also researched cluster validity for the fuzzy c-means model\cite{Bezdek1995}.
They researched what effect which parameters have on the validity of the clusters.
They specifically analyzed the role of weighting exponent \textit{m}(fuzziness parameter).
They concluded that the best choice for \textit{m} is probably in the interval [1.5, 2.5], whose mean and midpoint is \textit{m}=2.
Wu proposed a new guideline for selecting parameter \textit{m}\cite{Wu2012}.
His point of view was that a large \textit{m} value will make the fuzzy c-means more robust to noise and outliers.
He suggests implementing fuzzy c-means with \textit{m}=[1.5, 4].
When the data set contains noise and outliers, the fuzzifier\textit{m}=4 is recommended in a theoretical upper bound case.
Since our data set does not contain noise and outliers we choose to select the midpoint concluded in the research of Bezdek et al.\cite{Bezdek1995OnModel}.
The value of \textit{m} in this experiment is 2.
\newline
Finding the correct amount of clusters has been an ongoing problem for clustering algorithms\cite{Du2010Clustering:Approach}.
Fortunately there are some techniques available to estimate the cluster amount.
During model selection we discussed the mountain and subtractive models. 
These models are designed to estimate the amount of clusters in a data set.
The subtractive clustering model is specifically designed to approximate the number of clusters for fuzzy system models\cite{Chiu1994FuzzyEstimation}.
We will select and implement the subtractive clustering model to estimate the amount of clusters.
We can use this amount for the cluster amount parameter in the fuzzy c-means algorithm.

>>>>

\subsection{Algorithm parameters}
The fuzzy c-means algorithm has to initialize the centroids of the clusters.
Our selected library does this based on a random number.
It also allows us to control this random number.
To make the initialization of the centroid reproducible and deterministic we will use a generated seed.
The seed generated is included in the Github repository\cite{rbasarat-repo}.
\newline
Bezdek et al., also researched cluster validity for the fuzzy c-means model\cite{Bezdek1995OnModel}.
They researched what effect which parameters have on the validity of the clusters.
They specifically analyzed the role of weighting exponent \textit{m}(fuzziness parameter).
They concluded that the best choice for \textit{m} is probably in the interval [1.5, 2.5], whose mean and midpoint is \textit{m}=2.
Wu proposed a new guideline for selecting parameter \textit{m}\cite{Wu2012}.
His point of view was that a large \textit{m} value will make the fuzzy c-means more robust to noise and outliers.
He suggests implementing fuzzy c-means with \textit{m}=[1.5, 4].
When the data set contains noise and outliers, the fuzzifier\textit{m}=4 is recommended in a theoretical upper bound case.
Since our data set does not contain noise and outliers we choose to select the midpoint concluded in the research of Bezdek et al.\cite{Bezdek1995OnModel}.
The value of \textit{m} in this experiment is 2.
\newline
Finding the correct amount of clusters has been an ongoing problem for clustering algorithms\cite{Du2010Clustering:Approach}.
Fortunately there are some techniques available to estimate the cluster amount.
During model selection we discussed the mountain and subtractive models. 
These models are designed to estimate the amount of clusters in a data set.
The subtractive clustering model is specifically designed to approximate the number of clusters for fuzzy system models\cite{Chiu1994FuzzyEstimation}.
It approximates the centroids and amount of the clusters based on the data points in the data set\cite{Chiu1994FuzzyEstimation}.
We will select and implement the subtractive clustering model to estimate the amount of clusters.
We can use this amount for the cluster amount parameter in the fuzzy c-means algorithm.
